%----Required Packages and Functions----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=0.6cm, top=0.5cm, right=0.6cm, bottom=0.5cm}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}
\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}
{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

\newcommand{\resumeItem}[2]{
    \item{\textbf{#1}{:\hspace{0.5mm}#2 \vspace{-0.5mm}}}
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1},\hspace{0.3mm}#2 & \textit{\small{#3}} \end{tabular*}\vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\footnotesize{#4}} \\
    \textit{\footnotesize{#3}} &  \footnotesize{#2} \\
    \end{tabular*}\vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\footnotesize{#3}} \\
    \footnotesize{\textit{#2}} & \footnotesize{#4}\end{tabular*}\vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{\vspace{2mm}\begin{tcolorbox}\textbf{\large #1}\end{tcolorbox}\vspace{-4mm}}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
%-----End of Packages and Functions-------

%---------------INFORMATIONS------------------

\newcommand{\name}{Mehmet Emre Güneş}
\newcommand{\graduation}{Expected Graduation: May 2025}
\newcommand{\phone}{507 792 75 77}
\newcommand{\email}{emre.gunes@ug.bilkent.edu.tr}
\newcommand{\github}{memregn}
\newcommand{\linkedin}{mehmetemregunes}

\begin{document}
\fontfamily{cmr}\selectfont

%--------------HEADING--------------

\parbox{\dimexpr\linewidth \relax}
    {
    \begin{tabularx}{\linewidth}{L r}
    \textbf{\LARGE \name} & +90 \phone\\
    \graduation & \href{mailto:\email}{\email}\\
    {\href{https://w3.cs.bilkent.edu.tr/}{Bachelor of Science in Computer Science}} & \href{https://github.com/\github}{\textcolor{blue}{GitHub}} \\ 
    {\href{https://w3.bilkent.edu.tr/bilkent/}{Bilkent University, Ankara, Türkiye}} & \href{https://www.linkedin.com/in/\linkedin/}{\textcolor{blue}{LinkedIn}}
    \end{tabularx}
    }
\vspace{-2mm}

%-------------SUMMARY-----------------

\section{\textbf{Summary}}
    As a passionate and motivated final-year Computer Science student at Bilkent University, I am driven by a strong desire to learn new technologies, collaborate with diverse teams, and contribute innovative solutions. My expertise lies in coding, problem-solving, and continuous self-improvement. I am eager to apply my skills to real-world projects and am excited to gain further experience in the technology industry.
\vspace{-1mm}

%-----------EDUCATION-----------------

\section{\textbf{Education}}    
    \setlength{\tabcolsep}{5pt}
    \renewcommand{\arraystretch}{1.25}
    \small{\begin{tabularx}
    {\dimexpr\textwidth-0mm\relax}{|c|C|c|}
        \hline
            \textbf{Degree} & \textbf{School} & \textbf{Year} \\
        \hline
            BS in Computer Science & Bilkent University, Ankara, Türkiye & September 2020 - Present \\
        \hline
            Erasmus+ Programme & École supérieure d'informatique, électronique, automatique (ESIEA), Paris, France & September 2023 - January 2024 \\
        \hline
            High School & Eskişehir Anatolian High School, Eskişehir, Türkiye & September 2015 - June 2019 \\
        \hline
    \end{tabularx}}
\vspace{-1mm}

%--------------EXPERIENCE--------------------

\section{\textbf{Experience}}
    \resumeSubHeadingListStart
        \resumeProject
            {Yapı Kredi Teknoloji} {Part-time Software Engineering Intern}
            {September 2024 - Current} {Kocaeli, Türkiye}
                \resumeItemListStart
                    \item {Focused on integrating data from the legacy Application Inventory system into the newly designed structure. The front-end transition from JavaScript to {\textbf{TypeScript}} was completed, ensuring better type safety and maintainability.}
                    \item {Delivered presentations and demos to the team, introducing researched topics and exploring their integration into the Application Inventory system. Topics researched include Aspect-Oriented Programming, Kafka, RabbitMQ, Interceptor, Software Architecture Types, Nest.js, GraphQL, Drools, Keycloak, and Microsoft Workflow Foundation.}
                \resumeItemListEnd
        \resumeProject
            {Yapı Kredi Teknoloji} {Software Engineering Intern}
            {June 2024 - September 2024} {Kocaeli, Türkiye}
                \resumeItemListStart
                    \item {Worked as a {\textbf{Software Engineer Intern}} in the {\textbf{Corporate Architecture team}}, under the supervision of the {\textbf{Architectural Management}}, contributing to the development and enhancement of key systems such as the Application and Batch Inventory.}
                    \item {Developed and redesigned the {\textbf{Application Inventory}} system for Yapı Kredi Bank, showcasing all applications used within the bank. The back-end was implemented using {\textbf{Spring Boot}}, the front-end with {\textbf{React}}, and the database was designed and implemented using the {\textbf{Oracle database}}.}
                    \item {Conducted thorough testing on the Batch Inventory system, {\textbf{identifying and reporting}} several issues, including a few critical errors that had been previously overlooked. {\textbf{Detailed reports}} were provided to the relevant teams, ensuring timely resolution and improving the system's functionality.}
                \resumeItemListEnd
        \resumeProject
            {TUSAŞ Engine Industries, Inc.} {Information Technology Intern}
            {July 2023 - August 2023} {Eskişehir, Türkiye}
                \resumeItemListStart
                    \item {Gained experience in how {\textbf{Windows Server}}, {\textbf{Active Directory}}, and {\textbf{Computer Network}} are utilized within the company during my 24-day internship in the Information Technology department. Worked on setting up demos on the assigned Windows Server to learn and explore these topics.}
                \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-6.5mm}

%-----------TECHNICAL SKILLS-----------------

\section{\textbf{Technical Skills}}
\vspace{1mm}
    \resumeHeadingSkillStart
        \resumeSubItem{Programming Languages}
            {C, C++, Java, JavaScript, LaTeX, MIPS Assembly, Python, SQL, SystemVerilog, TypeScript}
        \resumeSubItem{Tools and Frameworks}
            {Android Studio, CLion, Drools, Firebase, Git, Github, GraphQL, Kafka, Keycloak, Lex, Mars, MySQL, PL/SQL, RabbitMQ, React, Vivado, VSCode, Yacc}
        \resumeSubItem{Operating Systems}
            {Android, Linux}
    \resumeHeadingSkillEnd
\vspace{-1mm}

%-----------PROJECTS-----------------

\section{\textbf{Projects}}
    \resumeSubHeadingListStart
        \resumeProject
            {Biletkent} {Database Systems (CS 353), Bilkent University}
            {January 2024 - May 2024} {\href{https://github.com/memregn/Biletkent}{\textbf{\color{blue}GitHub}}}
                \resumeItemListStart
                    \item {Biletkent is a ticket-purchasing application where organizers can add various events. Users can buy tickets for events such as concerts, theaters, stand-ups, and festivals. Admins can create events and see the statistics for all events.}
                    \item {{\textbf{HTML}} and {\textbf{CSS}} were used for the front-end. {\textbf{Flask-Python}} was used for the back end. {\textbf{MySQL}} was used for the database, which was facilitated by {\textbf{Docker}}. Changes made to the application's front-end and back-end were tested on the local server using Docker. This project was done with the {\textbf{teamwork}} of five people.}
                    \item {Keywords: \emph{CSS, Docker, Flask-Python, HTML, MySQL, teamwork}}
                \resumeItemListEnd
        \resumeProject
            {Siu} {Programming Languages (CS 315), Bilkent University}
            {March 2023 - April 2023} {\href{https://github.com/memregn/Siu}{\textbf{\color{blue}GitHub}}}
                \resumeItemListStart
                    \item {Siu is a new programming language in which only boolean type can be used. Includes complete {\textbf{BNF description}}, lexical analyzer {\textbf{Lex}}, and parser {\textbf{Yacc}} for Siu. This project was done with the {\textbf{teamwork}} of three people.}
                    \item {Keywords: \emph{BNF description, Lex, teamwork, Yacc}}
                \resumeItemListEnd
        \resumeProject
            {BilCat} {Algorithms and Programming II (CS 102), Bilkent University}
            {July 2021} {\href{https://github.com/memregn/BilCat}{\textbf{\color{blue}GitHub}}}
                \resumeItemListStart
                    \item {With BilCat, users can see the locations where cats are frequently seen living on the Bilkent University campus. Users can check the vaccinations of these cats. Users can mark the exact location where they see the cat and add its instant status as a comment. Users can see other users' comments on cats. This project was done with the {\textbf{teamwork}} of four people. }
                    \item {Developed on {\textbf{Android Studio}} using {\textbf{Java}} and {\textbf{XML}}. {\textbf{Firebase}} was used for the database. The project was managed on {\textbf{Github}}.}
                    \item {Keywords: \emph{Android, Android Studio, Firebase, Github, Java, XML, teamwork}}
                \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-6.5mm}

%-----------BOARD MEMBERSHIP-----------------

\section{\textbf{Board Membership}}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Social Awareness Projects (TDP) Organization}{Bilkent University, Ankara, Türkiye}
            {Coordinator}{January 2024 - June 2024}
                \resumeItemListStart
                    \item Planned and organized seminars, events, and bonding activities to increase the motivation of the volunteers and raise awareness about social issues like women and animal rights.
                    \item Organized a Children’s Fest that children can enjoy with the participation of 375 children and 160 volunteers.
                    \item Managed children, volunteers, and event places during the Children’s Fest and other events.
                \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-6.5mm}

%-----------VOLUNTEERING-----------------

\section{\textbf{Volunteering}}
    \resumeSubHeadingListStart
        \resumeSubheading
            {The Sun Rises from the Village (Günköy)}{Bilkent University, Ankara, Türkiye}
            {Volunteer}{September 2022 - Present}
                \resumeItemListStart
                    \item Participated in a project establishing libraries in rural schools. Attended {\textbf{four}} villages and participated in activities to enhance students' scientific, cultural, and artistic skills in village schools.
                \resumeItemListEnd
        \resumeSubheading
            {Social Awareness Projects (TDP) Organization}{Bilkent University, Ankara, Türkiye}
            {Volunteer}{January 2023 - June 2023}
                \resumeItemListStart
                    \item Actively volunteered in the Social Awareness Projects (TDP) Organization Subgroup.
                    \item Played a key role in preparing for the TDP Children’s Festival.
                \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-6.5mm}

%---------------LANGUAGES-------------------

\section{\textbf{Languages}}
\vspace{1.5mm}
    \resumeHeadingSkillStart
        \resumeSubItem{Turkish} {Native proficiency}
        \resumeSubItem{English} {Full professional proficiency}
        \resumeSubItem{French} {Elementary proficiency}
    \resumeHeadingSkillEnd

\vspace{-1mm}

%---------------CERTIFICATIONS-------------------

\section{\textbf{Certifications}}
\vspace{1mm}
    \resumeItemListStart
        \item {\textbf{React 301}} - Turkcell Geleceği Yazanlar, August 2024 {\href{https://drive.google.com/file/d/1IenyngMT2y_2hLJSEG-y8MHOHd0eRwbO/view?usp=sharing}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{React 201}} - Turkcell Geleceği Yazanlar, August 2024 {\href{https://drive.google.com/file/d/1CTlT4LIcoXtWq3MXYMbd_inrUtS2dtMO/view?usp=sharing}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{React 101}} - Turkcell Geleceği Yazanlar, July 2024 {\href{https://drive.google.com/file/d/12Yv9NWME4jnxaXeh3xz_NU6LCwiLmCBq/view?usp=sharing}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Advanced Java 301}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1GSBJzBw-dSaB3hQwN-c5BQGGdy20qW58/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Advanced Java 201}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1e7dPbrePcGrrI3544lBZZxP0abToFgE_/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Java 301}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1sKNB_yAps1XsJUGUAYD7-83D6pKqizfY/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{SQL 401}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1wTxdG7q5S2GMd0eEBudNcbIywe1suLhq/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{SQL 301}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1zV4tX2HmgFbVNMJ1mMnidrbv5uQRCh5A/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{SQL 201}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1a5EPsstzwkN3M9Z0G9QIZO8WxZcRtkNj/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{SQL 101}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1d1iOzdGYhEu5KoeWip_SZRFnxdsuqf6D/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Basic Linux 401}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1wpKyEhbPNQTZzwplEw6tVuWOwWNGz7zv/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Basic Linux 301}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1MMIma331bKIUi48JM1LeVoN7HqQyGvpa/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Basic Linux 201}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1ZjkmznYRdiaF7cU2sH9ctT_aDOPBavod/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Basic Linux 101}} - Turkcell Geleceği Yazanlar, June 2024 {\href{https://drive.google.com/file/d/1vxjC7sNosRZSfWmFjUxBFFtN8YMVDogF/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Advanced Java 101}} - Turkcell Geleceği Yazanlar, January 2024 {\href{https://drive.google.com/file/d/1aBq8jCQa5j_GXNiA9jb6-hDeL9MSDT6J/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Java 201}} - Turkcell Geleceği Yazanlar, January 2024 {\href{https://drive.google.com/file/d/1vD8vmiyYwKvS5aYOlA2uqjPI9n-wBM9T/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Java 101}} - Turkcell Geleceği Yazanlar, January 2024 {\href{https://drive.google.com/file/d/1zdZCYs2E5Qpped_xJRrILFj2uN1enebY/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Deep Learning Artificial Neural Networks}} - Turkcell Geleceği Yazanlar, August 2023 {\href{https://drive.google.com/file/d/16RW97XUNj9QyksCpjlbETMRPHho53KJg/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Basic Computer Network Course}} - Turkcell Geleceği Yazanlar, July 2023 {\href{https://drive.google.com/file/d/1c3lkospGb5_XNwzyL9Z_lm4VM06TJs1d/view?usp=drive_link}{\textbf{\color{blue}Certificate}}}
        \item {\textbf{Programming for Everybody (Getting Started with Python)}} - Coursera, January 2021 {\href{https://www.coursera.org/account/accomplishments/certificate/6EU4LEV48RQX}{\textbf{\color{blue}Certificate}}}
    \resumeItemListEnd
\vspace{-5.5mm}

%-------------------------------------------

\vfill
\center{\footnotesize Last updated: \today}

\end{document}